\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\ }}

### 2020-02-07 gwnnDraft02.tex
fixed language about alpha inf and alpha

%Explicitly, all exotic sectors (and heavy standard sectors) have strong first order phase transitions that lead to runaway bubble walls ($\alpha >\alpha_{\infty}$). 
Each component of the spectral energy density in Eq.~(\ref{eqn:SpectralEng}) is proportional to a power of their respective efficiency factors $\kappa$. The relative strength of the efficiency factors is dependent on the ratio $\frac{\alpha_{\infty}}{\alpha}$ --- since $\alpha_{\infty}$ is small, this would typically lead to the a scenario with runaway bublle walls where efficiency factors for the sound wave and MHD contributions are small and the GWs produced are dominantly from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$: this is what we assume for the remainder of this section. It should be noted, however, that $\alpha$ can also be small \cite{Bai:2018dxf,Helmboldt:2019pan}; this leads to bubbles that are non-runaway (but $v_w \sim 1$ still \cite{Breitbach:2018ddu,Bodeker2017}) such that non-bubble collision contributions being important --- ultimately leading to significant changes to the GW profile. This case and the gravitational waves it produces are examined in the appendix.

>>>>

%Explicitly, all exotic sectors (and heavy standard sectors) have strong first order phase transitions that lead to runaway bubble walls ($\alpha >\alpha_{\infty}$). 
Each component of the spectral energy density in Eq.~(\ref{eqn:SpectralEng}) is proportional to a power of their respective efficiency factors $\kappa$. The relative strength of the efficiency factors is dependent on the ratio $\frac{\alpha_{\infty}}{\alpha}$ --- since both $\alpha_{\infty}$ and $\alpha$ are parameterically small \cite{Bai:2018dxf,Helmboldt:2019pan} a range of possible scenarios can occur. Here, we discuss the two ends of this spectrum: pure runaway walls and pure non-runaway walls. The former scenario with runaway bublle walls leads to the efficiency factors for the sound wave and MHD contributions being small and ensures GWs are dominantly produced from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$: this is what we assume for the remainder of this section. In the latter case, bubbles are non-runaway (but $v_w \sim 1$ still \cite{Breitbach:2018ddu,Bodeker2017}) such that non-bubble collision contributions being important --- ultimately leading to significant changes to the GW profile. This case and the gravitational waves it produces are examined in the appendix. Intermediate results are of course possible, and would feature profiles somewhere in between the two extremes.
